Forklift: An Implementation of Nested Sampling for Two Objective Functions

### 2021-05-19 paper/ms.tex
A paragraph

>>>>

\section{NS with respect to one scalar}
Consider a simple problem where the parameter space is two dimensional,
the prior is
\begin{align}
x &\sim \textnormal{Exponential}(1) \\
y &\sim \textnormal{Exponential}(1),
\end{align}
and the two objective functions are also just $x$ and $y$ themselves.
If we were to run standard Nested Sampling on this problem, targeting
$x$, we would end up with points uniformly distributed along $x$ and
exponentially distributed along $y$ (in a frequency sense, with very high
prior probability).
